### 2021-02-18 architecture.tex
Architecture: Describe GCN (WIP)

>>>>

\subsection{\Gls{gcn}: From graphs to symbol embeddings}

For each symbol in the problem,
we seek to find a vector representation, i.e., an \emph{embedding},
that captures the symbol's properties that are relevant
for the desirable relative rank of the symbol in the symbol precedence.
The symbol embeddings are modeled by a \gls{rgcn} \cite{Schlichtkrull2017},
\todo{Can I use the term \gls{rgcn} when I use a modified version? Namely, the activation is called earlier.}
which is a stack of graph convolutional layers.
Each layer consists of a collection of differentiable modules --- one for each edge type.
A pass through the convolutional layer takes the embeddings of all symbols,
converts them by the edge modules of the adjacent edges to form the messages,
passes the messages to the destination nodes
and aggregates the incoming messages of each node.
In the simple case that each edge module is a dense layer,
the output embeddings $h^{(l+1)}$ is computed from the input embeddings $h^{(l)}$ in the following manner:
$$
h_i^{(l+1)} =
\sum_{r \in \mathcal{R}} \sigma \Parentheses{\sum_{j \in \mathcal{N}_i^r} \frac{1}{c_{ji}} h_j^{(l)} W_r^{(l)}}
$$
%$$
%h_i^{(l+1)} =
%\mathrm{LayerNorm} \Parentheses{h_i^{(l)} + \sum_{r \in \mathcal{R}} \sigma \Parentheses{\sum_{j \in %\mathcal{N}_i^r} \frac{1}{c_{ji}} h_j^{(l)} W_r^{(l)}}}
%$$
% Inspiration: https://ufal.mff.cuni.cz/~straka/courses/npfl114/1920/slides.pdf/npfl114-07.pdf - slide 27 - Transformer
\todo{FB: Mention inspiration: Transformer. See Straka's slides.}
$h_i^{(l)}$ denotes the embedding of node $i$ at layer $l$.
$\mathcal{R}$ denotes the set of all relations in the graph.
$\sigma$ denotes the activation function, for example the \gls{relu}.
$\mathcal{N}_i^r$ denotes the set of neighbors of node $i$ under relation $r$.
$c_{j, i, r} = \sqrt{\card{\mathcal{N}_j^r}} \sqrt{\card{\mathcal{N}_i^r}}$ is a normalization constant \cite{kipf2017semisupervised}.
$W_r^{(l)}$ is a trainable weight matrix representing relation $r$ at layer $l$.

\todo[inline]{Explain residual connections and layer normalization.}
\todo[inline]{MS: neni uplne jiste, ze ``CADE people'' oceni presny zapis 
strutury site, vcetne prvku jako $\mathrm{LayerNorm}$ ve vzorecku.
Nerikam, ze bychom to meli uplne zatajit, ale popis, ktery je zde, spis
patri do appendixu (ML paperu). Na te siti vlastne nic originalniho neni,
tak neni treba vsechno vysvetlit do detailu. Zajimavejsi tu
potom je az to, jak se problem $P$ ``otiskne'' v topologii grafu. 
To uz originalni je (a soutezi to s representacemi jako ta Mirkova)
a popisujes to pak dal.}
